---
title: "Plotly_ex"
author: "Aleksey Butylev"
date: '2 June 2017'
output: ioslides_presentation
---

```{r setup, include=FALSE}
  knitr::opts_chunk$set(echo = FALSE)
  library(plotly); library(ggplot2)
  alldata <- read.csv(file = 'PlotlyData.csv', header = T, sep = ';')
  alldata$Income <- alldata$Income/1000
  alldata$Date <- as.Date(alldata$Date, "%d.%m.%Y")
  alldata$size <- log(alldata$Quantity)/10
```


## Week 3 assignment - Plotly Presentation {.smaller}

This presentation demonstrates animated plot, which uses key frame animations through the **frame** attribute/aesthetic.

The plot shows the Quantity vs Income graph of different groups of customers. These groups are:

 - New clients (who became clients less than 3 months ago)

 - Developing clients (those who are clients for 3-9 months)

 - Active clients (> 9 months of experience)

 - Declining clients (who shows falling incomes)

 - Sleeping clients (no income at all)

 - Lost clients (no income more than 3 months)</small>


## Customer groups

```{r plot}
  base <- alldata %>% plot_ly(x = ~Quantity, y = ~Income, legendgroup = ~Stage,  
                               text = ~Stage, hoverinfo = 'text+x+y', sizes = c(10, 30)) %>%
      ##add_markers(color = I("black"), alpha = 0.01) %>%
      add_markers(color = ~Stage, frame = ~Date, size = ~size, ids = ~Stage) %>%
      ## add_trace(color = ~Stage, frame = ~Date, inherit = T) %>%
      animation_opts(1000, easing = "elastic", redraw = FALSE) %>%
      animation_button(
        x = 1, xanchor = "right", y = 0, yanchor = "bottom"
     ) %>%
  animation_slider(
  currentvalue = list(prefix = "YEAR ", font = list(color="red"))
  )
  base
```

## Thank you!

